Late Pleistocene stone artefact technology at Mau A, Yen Bai, Norther Vietnam

### 2022-03-04 analysis/paper/paper.Rmd
I noticed an error with our contribution plots. See discussion section for comment.

Looking at \@ref(fig:contribution-plots), one can see that

>>>>

 <!-- QH: As I write this I notice a major issue with the axes labels on the contribution plots. Instead of substituting the original labels on a one to one basis with our English labels, our plots are just printing out our list of English labels in the order they are listed in our code. This has to be fixed. I then need to redo my description of the plots, since it is all wrong and based off of the eroneous labels. -->

Looking at \@ref(fig:contribution-plots), the landmarks which contributed the most to each principal component were all located on the left side of our artefacts. This means that linking our initial flake measurements (maximum length, top width etc.) to either of the first two principal components is nearly impossible, as every one of our initial flake measurements (with the)

one can see that there is no consistent pattern in which certain initial flake measurements  align closely with either the first or second principal components. Interestingly, the landmarks which contributed the most to each principal component were all located on the left side of our artefacts..
